One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-11-30 submissions/differences_initial_vs_revision_2/manuscript.tex
revision 2

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%
One-dimensional turbulence (ODT) is an accurate and computationally efficient technique for modeling turbulent flows. ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows. Applications include use as a standalone model and as a closure for large-eddy simulation (LES). Its strength lies in the ability to capture a full range of turbulent length and time scales. The ODT model is strongly coupled with its implementation, complicating its formulations. We present a modern, open-source, object-oriented C++ implementation of ODT. This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.
%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Early applications of ODT focused on homogeneous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}. Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames \cite{Echekki_2001,Hewson_2001,Hewson_2002,Lignell_2012,Punati_2011,Abdelsamie_2017,Lignell_2017, Goshayeshi_2015}, counterflow flames \cite{Jozefik_2015}, wall fires \cite{Monson_2016}, and sooting flames \cite{Lignell_2015,Hewson_2006,Hewson_2009,Lignell_2015b,Ricks_2010}, as well as other particle flows \cite{Sun_2017,Schmidt_2009,Sun_2014,Fistler_2017}. ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}. Most recently, the ODT code was extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.

During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration. The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions. The example case in Section~\ref{sec:examples} is a representative sample of the ODT code's capabilities as it is presented here. Future releases will expand this code's functionality with additional features currently in development.

@@

The ODT model is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here. In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy. The ODT code uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.

@@

Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations. In this way, the ODT code marches in time or space until it reaches the simulation end point. Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters. In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations. This is done via post-processing tools, which are provided in the ODT package.

@@

The ODT package consists primarily of an object-oriented C++ code responsible for running flow simulation cases and generating data. The package also contains auxiliary data processing and visualization tools, written mostly in Python. The post-processing tools are case-specific but will be  addressed generally in Section~\ref{sub:workflow}.

@@

This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation. ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface. For more details, please see the package documentation.

Within the main download package, several directories organize the ODT code. The \texttt{source}, \texttt{build}, and \texttt{run} directories contain the ODT source code, compilation tools, and run scripts, respectively. The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with the appropriate input files. The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated by ODT, as well as post-processed data files generated from within the \texttt{post} directory. Finally, the \texttt{docs} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.

\subsubsection{Building ODT}

The ODT build process is automated with CMake. The user navigates to the \texttt{build} directory and edits the CMake configuration file. The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location. For reacting flows, the chemical reaction rates can be computed by Cantera (default), or a from a user-specified function, specified at compile time. Once the configuration settings are updated, the user runs CMake to apply the changes.

The \texttt{yaml-cpp} package is required in order to process input files. If it has not yet been installed, it must be built and installed at this point. For convenience, the ODT package automates this process. YAML need only be installed once for a given instance of the ODT package. Rebuilding the ODT code with CMake does not affect the YAML installation.

@@

User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT. At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.

The \texttt{input} directory also contains the \texttt{gas\textunderscore mechanisms} subdirectory, which contains chemical mechanism files that can be used in reacting flow cases. For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in \texttt{input.yaml}. Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the ODT build process.

@@

\subsubsection{Running ODT}

@@

@@

ODT is uniquely suited to reacting flow simulations. Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al. \cite{Meier_2000}. This canonical flame configuration has been used extensively to study and validate turbulent combustion models \cite{Pitsch_2000,Lindstedt_2005,Wang_2011,Fairweather_2004,Lee_2008,Lee_2009}.

@@

Previous ODT studies of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration. This simulation uses the experimentally reported velocity profiles and jet dimensions.  
The fuel was diluted with N$_2$ in the experimental flame to minimize radiative heat losses, and radiation is ignored in the simulation. This flame has a low Reynolds number, and the combustion chemistry proceeds quickly. The ODT simulation transports the chemical species O$_2$, N$_2$, CH$_4$, H$_2$, H$_2$O, and CO$_2$. We assume that reactions proceed to the products of complete combustion and apply simple, fast reaction rates according to the following chemical equations:
\begin{align}
	\mathrm{CH}_4 + 2\mathrm{O}_2 & \rightarrow \mathrm{CO}_2 + 2\mathrm{H}_2\mathrm{O}, \\
	\mathrm{H}_2+\frac{1}{2}\mathrm{O}_2 & \rightarrow \mathrm{H}_2\mathrm{O}.
\end{align}
These assumptions are reasonable for illustrating ODT in the DLR-A reacting jet configuration with variable properties and heat release.

@@

Figure~\ref{fig:dlr_example_results} displays the simulation results: axial mean and centerline values for (a) axial velocity $v$, (b) mixture fraction $\xi$, and (c) temperature $T$. The ODT results track the experimental data well for all three variables. The centerline temperature peaks about 100 K above the experimental data, but this small difference can be attributed to thermal radiation (which was neglected in this simulation) and the assumption that reactions proceed to the products of complete combustion rather than their equilibrium state. The centerline velocity shows a fast initial decrease that can be attributed to diffusion. Similarly, the increase in centerline velocity RMS values is delayed; this occurs due to the elapsed time model for large eddy suppression, which limits disturbances in the early stages of the flow to small eddies that occur on the jet edges away from the centerline.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Impact}
\label{sec:impact}
The ODT model is complex, challenging to implement, and difficult to cleanly separate from its implementation, all of which presents barriers to practitioners who wish to use the model. For instance, triplet mapa can be represented mathematically but are usually implemented as previously described, assuming an adaptive grid with variable cell sizes. Alternative formulations are used for fixed grids. The code presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals. Its structure facilitates addressing new research questions, such as soot-flame-radiation-chemistry interactions, multi-phase reacting flows using Lagrangian particle models (such as diesel sprays), and coupled near-wall heat and momentum transfer. The code presented here has been extended to and demonstrated in such systems already, facilitated by the object-oriented structure. For example, this code has been extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.

@@

@@

\bibitem{Lignell_2015}
D.~O. Lignell, G.~C. Fredline, A.~D. Lewis, Comparison of one-dimensional
  turbulence and direct numerical simulations of soot formation and transport
  in a nonpremixed ethylene jet flame 35~(2) (2015) 1199--1206.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.05.046}
  {\path{doi:10.1016/j.proci.2014.05.046}}.

\bibitem{Abboud_2015}
A.~W. Abboud, C.~Schulz, T.~Saad, S.~T. Smith, D.~D. Harris, D.~O. Lignell, A
  numerical comparison of precipitating turbulent flows between large-eddy
  simulation and one-dimensional turbulence 61~(10) (2015) 3185--3197.
\newblock \href {http://dx.doi.org/10.1002/aic.14870}
  {\path{doi:10.1002/aic.14870}}.

\bibitem{Kerstein_1999}
A.~R. Kerstein, One-dimensional turbulence: model formulation and application
  to homogeneous turbulence, shear flows, and buoyant stratified flows 392
  (1999) 277--334.
\newblock \href {http://dx.doi.org/10.1017/S0022112099005376}
  {\path{doi:10.1017/S0022112099005376}}.

\bibitem{Kerstein_2000}
A.~R. Kerstein, T.~D. Dreeben, Prediction of turbulent free shear flow
  statistics using a simple stochastic model 12~(2) (2000) 418--424.
\newblock \href {http://dx.doi.org/10.1063/1.870319}
  {\path{doi:10.1063/1.870319}}.

\bibitem{Kerstein_2001}
A.~R. Kerstein, W.~T. Ashurst, S.~Wunsch, V.~Nilsen, One-dimensional
  turbulence: vector formulation and application to free shear flows 447 (2001)
  85--109.
\newblock \href {http://dx.doi.org/10.1017/S0022112001005778}
  {\path{doi:10.1017/S0022112001005778}}.

\bibitem{Echekki_2001}
T.~Echekki, A.~R. Kerstein, T.~D. Dreeben, J.-Y. Chen, `one-dimensional
  turbulence' simulation of turbulent jet diffusion flames: model formulation
  and illustrative applications 125~(3) (2001) 1083--1105.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00228-0}
  {\path{doi:10.1016/S0010-2180(01)00228-0}}.

\bibitem{Hewson_2001}
J.~C. Hewson, A.~R. Kerstein, Stochastic simulation of transport and chemical
  kinetics in turbulent
  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames 5~(4)
  (2001) 669--697.
\newblock \href {http://dx.doi.org/10.1088/1364-7830/5/4/309}
  {\path{doi:10.1088/1364-7830/5/4/309}}.

\bibitem{Hewson_2002}
J.~C. Hewson, A.~R. Kerstein, Local extinction and reignition in nonpremixed
  turbulent {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet
  flames 174~(5-6) (2002) 35--66.
\newblock \href {http://dx.doi.org/10.1080/713713031}
  {\path{doi:10.1080/713713031}}.

\bibitem{Lignell_2012}
D.~O. Lignell, D.~S. Rappleye, One-dimensional-turbulence simulation of flame
  extinction and reignition in planar ethylene jet flames 159~(9) (2012)
  2930--2943.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2012.03.018}
  {\path{doi:10.1016/j.combustflame.2012.03.018}}.

\bibitem{Punati_2011}
N.~Punati, J.~C. Sutherland, A.~R. Kerstein, E.~R. Hawkes, J.~H. Chen, An
  evaluation of the one-dimensional turbulence model: comparison with direct
  numerical simulations of {CO}/{H}\textsubscript{2 }jets with extinction and
  reignition 33~(1) (2011) 1515--1522.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.06.127}
  {\path{doi:10.1016/j.proci.2010.06.127}}.

\bibitem{Abdelsamie_2017}
A.~Abdelsamie, D.~O. Lignell, D.~Th{\'e}venin, Comparison between {ODT} and
  {DNS} for ignition occurrence in turbulent premixed jet combustion:
  safety-relevant applications 231~(10) (2017) 1709--1735.
\newblock \href {http://dx.doi.org/10.1515/zpch-2016-0902}
  {\path{doi:10.1515/zpch-2016-0902}}.

@@

\bibitem{Goshayeshi_2015}
B.~Goshayeshi, J.~C. Sutherland, Prediction of oxy-coal flame stand-off using
  high-fidelity thermochemical models and the one-dimensional turbulence model
  35~(3) (2015) 2829--2837.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.07.003}
  {\path{doi:10.1016/j.proci.2014.07.003}}.

\bibitem{Jozefik_2015}
Z.~Jozefik, A.~R. Kerstein, H.~Schmidt, S.~Lyra, H.~Kolla, J.~H. Chen,
  One-dimensional turbulence modeling of a turbulent counterflow flame with
  comparison to {DNS} 162~(8) (2015) 2999--3015.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2015.05.010}
  {\path{doi:10.1016/j.combustflame.2015.05.010}}.

\bibitem{Monson_2016}
E.~I. Monson, D.~O. Lignell, M.~A. Finney, C.~Werner, Z.~Jozefik, A.~R.
  Kerstein, R.~S. Hintze, Simulation of ethylene wall fires using the
  spatially-evolving one-dimensional turbulence model 52~(1) (2016) 167--196.
\newblock \href {http://dx.doi.org/10.1007/s10694-014-0441-2}
  {\path{doi:10.1007/s10694-014-0441-2}}.

@@

\bibitem{Ricks_2010}
A.~J. Ricks, J.~C. Hewson, A.~R. Kerstein, J.~P. Gore, S.~R. Tieszen, W.~T.
  Ashurst, A spatially developing one-dimensional turbulence ({ODT}) study of
  soot and enthalpy evolution in meter-scale buoyant turbulent flames 182~(1)
  (2010) 60--101.
\newblock \href {http://dx.doi.org/10.1080/00102200903297003}
  {\path{doi:10.1080/00102200903297003}}.

\bibitem{Sun_2017}
G.~Sun, J.~C. Hewson, D.~O. Lignell, Evaluation of stochastic particle
  dispersion modeling in turbulent round jets 89 (2017) 108--122.
\newblock \href {http://dx.doi.org/10.1016/j.ijmultiphaseflow.2016.10.005}
  {\path{doi:10.1016/j.ijmultiphaseflow.2016.10.005}}.

\bibitem{Schmidt_2009}
J.~R. Schmidt, J.~O.~L. Wendt, A.~R. Kerstein, Non-equilibrium wall deposition
  of inertial particles in turbulent flow 137~(2) (2009) 233--257.
\newblock \href {http://dx.doi.org/10.1007/s10955-009-9844-8}
  {\path{doi:10.1007/s10955-009-9844-8}}.

>>>>

%\usepackage{soul}
%\usepackage{color}
\usepackage{changes}
\colorlet{Changes@Color}{yellow}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%
    One-dimensional turbulence (ODT) is an accurate and computationally efficient \deleted{technique} \added{model} for \deleted{modeling} \added{simulating} turbulent flows. ODT has been applied to a wide range of flow problems including reaction, multiphase, differential diffusion, heat release, buoyancy, and wall flows. Applications include use as a standalone model and as a closure for large-eddy simulation (LES). Its strength lies in the ability to capture a full range of turbulent length and time scales. The ODT model is strongly coupled with its implementation, complicating its formulations. We present a modern, open-source, object-oriented C++ implementation of ODT. \deleted{This code can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.} \added{The code described here and made available online can be used as a starting point to understand, apply, and extend the ODT model, enabling its further application to turbulent flow research.}
%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Early applications of ODT focused on homogeneous turbulence, wakes, and mixing layers \cite{Kerstein_1999,Kerstein_2000,Kerstein_2001}. Later extension to variable-density flows and a spatial downstream coordinate system facilitated its growth and application to more complex flows, including combustion in jet flames \cite{Echekki_2001,Hewson_2001,Hewson_2002,Lignell_2012,Punati_2011,Abdelsamie_2017,Lignell_2017, Goshayeshi_2015}, counterflow flames \cite{Jozefik_2015}, wall fires \cite{Monson_2016}, and sooting flames \cite{Lignell_2015,Hewson_2006,Hewson_2009,Lignell_2015b,Ricks_2010}, as well as other particle flows \cite{Sun_2017,Schmidt_2009,Sun_2014,Fistler_2017}. ODT has also served to complement LES through subgrid modeling studies \cite{Cao_2008,Schmidt_2003,Schmidt_2010} and has been applied to various other flow configurations such as double-diffusive interfaces \cite{GonzalezJuez_2011}, Rayleigh-Taylor mixing \cite{GonzalezJuez_2013}, and stratified turbulence \cite{Wunsch_2001}. Most recently, \deleted{the ODT code was} \added{ODT implementations have been} extended to include cylindrical and spherical coordinate systems \cite{Lignell_2018,Klein_2018,Klein_2019}.

\deleted{During the recent implementation of the cylindrical and spherical model formulations, the ODT code was drastically overhauled and reorganized, resulting in its current configuration. } \added{Many of the references cited above make use of a particular software implementation of the ODT model, referred to here as the \emph{ODT code}. During the recent implementation of the cylindrical and spherical model formulations, this code was drastically overhauled and reorganized.} The ODT code presented here is a pared down version of the development code, representing the fundamental aspects of the ODT model and its most reliable functions. The example case in Section~\ref{sec:examples} is a representative sample of the ODT code's capabilities as it is presented here. Future releases will expand this code's functionality with additional features currently in development.

@@

The ODT model \added{formulation} is described in detail in the literature~\cite{Kerstein_1999,Kerstein_2001,Ashurst_2005,Lignell_2018,Lignell_2013}; only a brief explanation will be given here. In ODT, turbulent advection is modeled with stochastic processes called eddy events, which punctuate the solution of unsteady, one-dimensional transport equations for mass, momentum, and enthalpy. The ODT code \added{implementation of the ODT model} uses a Lagrangian finite-volume formulation for diffusive advancement in which mass stays constant within each grid cell while cell volumes increase or decrease according to cell dilation via an adaptive mesh refinement~\cite{Lignell_2013}.

@@

Eddy events occur concurrently with diffusive advancement via solution of the system of unsteady one-dimensional transport equations. In this way, the ODT code marches in time or space until it reaches the simulation end point. Due to the stochastic nature of eddy events, each ODT simulation, or realization, is different, even when it is provided with the same input parameters. In order to obtain statistically stable data for a given set of parameters, we run many realizations with the same input parameters and then gather statistics over these realizations. This is done via post-processing tools. Post-processing is specific to a given case and the needs of the user. Examples of post-processing files are included for different cases provided with the ODT code, as discussed further in Section~\ref{sec:data_files_post_processing}.

@@

The ODT code package consists primarily of an object-oriented C++ code responsible for running flow simulation cases and generating data. The package also contains auxiliary data processing and visualization tools, written mostly in Python. The post-processing tools are case-specific but will be  addressed generally in Section~\ref{sub:workflow}.

@@

This section outlines the process a user goes through in order to successfully build the ODT code and run a simulation. The ODT \added{code} is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface. For more details, please see the package documentation.

Within the main download package, several directories organize the ODT code. The \texttt{source}, \texttt{build}, and \texttt{run} directories contain the ODT source code, compilation tools, and run scripts, respectively. The \texttt{input} directory contains subdirectories corresponding to several possible case types, each populated with the appropriate input files. The \texttt{data} directory, initially empty, holds the raw data files and runtime information generated \deleted{by ODT}, as well as post-processed data files generated from within the \texttt{post} directory. Finally, the \texttt{docs} directory contains documentation optionally generated by Doxygen \cite{vanHeesch_2018} during the build process.

\subsubsection{Building \deleted{ODT} \added{the ODT code}}

The ODT \added{code} build process is automated with CMake. The user navigates to the \texttt{build} directory and edits the CMake configuration file. The CMake configuration file specifies Cantera's location and must be changed to reflect the local installation location. For reacting flows, the chemical reaction rates can be computed by Cantera (default), or a from a user-specified function, specified at compile time. Once the configuration settings are updated, the user runs CMake to apply the changes.

The \texttt{yaml-cpp} package is required in order to process input files. If it has not yet been installed, it must be built and installed at this point. For convenience, the ODT \added{code} package automates this process. YAML need only be installed once for a given instance of the ODT package. Rebuilding the ODT code with CMake does not affect the YAML installation.

@@

User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run \deleted{with ODT}. At minimum, a case's subdirectory must contain an \texttt{input.yaml} file, but may contain other files, or subfolders with supplementary information.

The \texttt{input} directory also contains the \texttt{gas\textunderscore mechanisms} subdirectory, which contains chemical mechanism files that can be used in reacting flow cases. For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in \texttt{input.yaml}. Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the CMake configuration file during the \deleted{ODT} build process.

@@

\subsubsection{Running \deleted{ODT} \added{the ODT code}}

@@

As part of the post-processing tools, there is a \texttt{post/tools} directory that contains two files: \texttt{data\_py.py} and \texttt{data\_tools.py}. The first of these can be used to convert the text data files generated during a run into binary numpy files. This can reduce both the number of data files and the file sizes. The number of files is reduced since all code realizations at a given output time are saved in the same binary file. The \texttt{data\_tools.py} file is a module that contains a number of functions for processing the data files, such as functions to
%
\begin{itemize}
    \item get the data from a given realization,
    \item return the number of realizations,
    \item get a list of the variable names in the data files,
    \item compute axial locations in the spatial ODT formulation,
    \item query a parameter from the input file,
    \item return the stoichiometric mixture fraction for combustion/mixing problems, and
    \item compute the domain bounds.
\end{itemize}
%
In addition, a few functions are provided for doing interpolation/extrapolation, and computing probability denisity functions (PDFs), and weighted PDFs.
Many of these functions take an argument that is a dictionary of case-specific information, such as the case name and paths for key directories. This dictionary is set in the post-processing driver script based only on the user-specified case name.

@@

\deleted{ODT} \added{The ODT model} is uniquely suited to reacting flow simulations. Here, we present illustrative ODT simulation results of a round, turbulent jet flame based on and compared to the experimental DLR-A flame of Meier et al. \cite{Meier_2000}. This canonical flame configuration has been used extensively to study and validate turbulent combustion models \cite{Pitsch_2000,Lindstedt_2005,Wang_2011,Fairweather_2004,Lee_2008,Lee_2009}.

@@

Previous ODT \deleted{studies} \added{simulations} of turbulent jet flames have used the temporal planar formulation, but the spatial cylindrical formulation developed recently \cite{Lignell_2018} more closely matches the experimental configuration. This simulation uses the experimentally reported velocity profiles and jet dimensions.  
The fuel was diluted with N$_2$ in the experimental flame to minimize radiative heat losses, and radiation is ignored in the simulation. This flame has a low Reynolds number, and the combustion chemistry proceeds quickly. The ODT simulation transports the chemical species O$_2$, N$_2$, CH$_4$, H$_2$, H$_2$O, and CO$_2$. We assume that reactions proceed to the products of complete combustion and apply simple, fast reaction rates according to the following chemical equations:
\begin{align}
	\mathrm{CH}_4 + 2\mathrm{O}_2 & \rightarrow \mathrm{CO}_2 + 2\mathrm{H}_2\mathrm{O}, \\
	\mathrm{H}_2+\frac{1}{2}\mathrm{O}_2 & \rightarrow \mathrm{H}_2\mathrm{O}.
\end{align}
These assumptions are reasonable for illustrating ODT in the DLR-A reacting jet configuration with variable properties and heat release.

@@

Figure~\ref{fig:dlr_example_results} displays the simulation results: axial mean and centerline values for (a) axial velocity $v$, (b) mixture fraction $\xi$, and (c) temperature $T$. The ODT \added{simulation} results track the experimental data well for all three variables. The centerline temperature peaks about 100 K above the experimental data, but this small difference can be attributed to thermal radiation (which was neglected in this simulation) and the assumption that reactions proceed to the products of complete combustion rather than their equilibrium state. The centerline velocity shows a fast initial decrease that can be attributed to diffusion. Similarly, the increase in centerline velocity RMS values is delayed; this occurs due to the elapsed time model for large eddy suppression, which limits disturbances in the early stages of the flow to small eddies that occur on the jet edges away from the centerline.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Impact}
\label{sec:impact}
The ODT model is complex, challenging to implement, and difficult to cleanly separate from its implementation, all of which presents barriers to practitioners who wish to use the model. For instance, triplet mapa can be represented mathematically but are usually implemented as previously described, assuming an adaptive grid with variable cell sizes. Alternative formulations are used for fixed grids. The \deleted{code} \added{ODT code implementation} presented here reduces these barriers by providing an open-source, well-documented, modularly styled code that can be used directly or modified to suit particular research goals. Its structure facilitates addressing new research questions, such as soot-flame-radiation-chemistry interactions, multi-phase reacting flows using Lagrangian particle models (such as diesel sprays), and coupled near-wall heat and momentum transfer. The code presented here has been extended to and demonstrated in such systems already, facilitated by the object-oriented structure. For example, this code has been extended to solve steady laminar flamelets \cite{Peters_1984}, requiring inheritance from the \texttt{solver}, \texttt{micromixer}, and \texttt{dv} (domain variable) classes.

@@

%\bibliographystyle{elsarticle-num} 
%\bibliography{references}

@@

\bibitem{Lignell_2015}
D.~O. Lignell, G.~C. Fredline, A.~D. Lewis, Comparison of one-dimensional
  turbulence and direct numerical simulations of soot formation and transport
  in a nonpremixed ethylene jet flame, Proceedings of the Combustion Institute
  35~(2) (2015) 1199--1206.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.05.046}
  {\path{doi:10.1016/j.proci.2014.05.046}}.

\bibitem{Abboud_2015}
A.~W. Abboud, C.~Schulz, T.~Saad, S.~T. Smith, D.~D. Harris, D.~O. Lignell, A
  numerical comparison of precipitating turbulent flows between large-eddy
  simulation and one-dimensional turbulence, AIChE Journal 61~(10) (2015)
  3185--3197.
\newblock \href {http://dx.doi.org/10.1002/aic.14870}
  {\path{doi:10.1002/aic.14870}}.

\bibitem{Kerstein_1999}
A.~R. Kerstein, One-dimensional turbulence: model formulation and application
  to homogeneous turbulence, shear flows, and buoyant stratified flows, Journal
  of Fluid Mechanics 392 (1999) 277--334.
\newblock \href {http://dx.doi.org/10.1017/S0022112099005376}
  {\path{doi:10.1017/S0022112099005376}}.

\bibitem{Kerstein_2000}
A.~R. Kerstein, T.~D. Dreeben, Prediction of turbulent free shear flow
  statistics using a simple stochastic model, Physics of Fluids 12~(2) (2000)
  418--424.
\newblock \href {http://dx.doi.org/10.1063/1.870319}
  {\path{doi:10.1063/1.870319}}.

\bibitem{Kerstein_2001}
A.~R. Kerstein, W.~T. Ashurst, S.~Wunsch, V.~Nilsen, One-dimensional
  turbulence: vector formulation and application to free shear flows, Journal
  of Fluid Mechanics 447 (2001) 85--109.
\newblock \href {http://dx.doi.org/10.1017/S0022112001005778}
  {\path{doi:10.1017/S0022112001005778}}.

\bibitem{Echekki_2001}
T.~Echekki, A.~R. Kerstein, T.~D. Dreeben, J.-Y. Chen, `one-dimensional
  turbulence' simulation of turbulent jet diffusion flames: model formulation
  and illustrative applications, Combustion and Flame 125~(3) (2001)
  1083--1105.
\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00228-0}
  {\path{doi:10.1016/S0010-2180(01)00228-0}}.

\bibitem{Hewson_2001}
J.~C. Hewson, A.~R. Kerstein, Stochastic simulation of transport and chemical
  kinetics in turbulent
  {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2 }flames,
  Combustion Theory and Modelling 5~(4) (2001) 669--697.
\newblock \href {http://dx.doi.org/10.1088/1364-7830/5/4/309}
  {\path{doi:10.1088/1364-7830/5/4/309}}.

\bibitem{Hewson_2002}
J.~C. Hewson, A.~R. Kerstein, Local extinction and reignition in nonpremixed
  turbulent {CH}\textsubscript{4}/{H}\textsubscript{2}/{N}\textsubscript{2} jet
  flames, Combustion Science and Technology 174~(5-6) (2002) 35--66.
\newblock \href {http://dx.doi.org/10.1080/713713031}
  {\path{doi:10.1080/713713031}}.

\bibitem{Lignell_2012}
D.~O. Lignell, D.~S. Rappleye, One-dimensional-turbulence simulation of flame
  extinction and reignition in planar ethylene jet flames, Combustion and Flame
  159~(9) (2012) 2930--2943.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2012.03.018}
  {\path{doi:10.1016/j.combustflame.2012.03.018}}.

\bibitem{Punati_2011}
N.~Punati, J.~C. Sutherland, A.~R. Kerstein, E.~R. Hawkes, J.~H. Chen, An
  evaluation of the one-dimensional turbulence model: comparison with direct
  numerical simulations of {CO}/{H}\textsubscript{2 }jets with extinction and
  reignition, Proceedings of the Combustion Institute 33~(1) (2011) 1515--1522.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2010.06.127}
  {\path{doi:10.1016/j.proci.2010.06.127}}.

\bibitem{Abdelsamie_2017}
A.~Abdelsamie, D.~O. Lignell, D.~Th{\'e}venin, Comparison between {ODT} and
  {DNS} for ignition occurrence in turbulent premixed jet combustion:
  safety-relevant applications, Zeitschrift fur Physikalische Chemie 231~(10)
  (2017) 1709--1735.
\newblock \href {http://dx.doi.org/10.1515/zpch-2016-0902}
  {\path{doi:10.1515/zpch-2016-0902}}.

@@

\bibitem{Goshayeshi_2015}
B.~Goshayeshi, J.~C. Sutherland, Prediction of oxy-coal flame stand-off using
  high-fidelity thermochemical models and the one-dimensional turbulence model,
  Proceedings of the Combustion Institute 35~(3) (2015) 2829--2837.
\newblock \href {http://dx.doi.org/10.1016/j.proci.2014.07.003}
  {\path{doi:10.1016/j.proci.2014.07.003}}.

\bibitem{Jozefik_2015}
Z.~Jozefik, A.~R. Kerstein, H.~Schmidt, S.~Lyra, H.~Kolla, J.~H. Chen,
  One-dimensional turbulence modeling of a turbulent counterflow flame with
  comparison to {DNS}, Combustion and Flame 162~(8) (2015) 2999--3015.
\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2015.05.010}
  {\path{doi:10.1016/j.combustflame.2015.05.010}}.

\bibitem{Monson_2016}
E.~I. Monson, D.~O. Lignell, M.~A. Finney, C.~Werner, Z.~Jozefik, A.~R.
  Kerstein, R.~S. Hintze, Simulation of ethylene wall fires using the
  spatially-evolving one-dimensional turbulence model, Fire Technology 52~(1)
  (2016) 167--196.
\newblock \href {http://dx.doi.org/10.1007/s10694-014-0441-2}
  {\path{doi:10.1007/s10694-014-0441-2}}.

@@

\bibitem{Ricks_2010}
A.~J. Ricks, J.~C. Hewson, A.~R. Kerstein, J.~P. Gore, S.~R. Tieszen, W.~T.
  Ashurst, A spatially developing one-dimensional turbulence ({ODT}) study of
  soot and enthalpy evolution in meter-scale buoyant turbulent flames,
  Combustion Science and Technology 182~(1) (2010) 60--101.
\newblock \href {http://dx.doi.org/10.1080/00102200903297003}
  {\path{doi:10.1080/00102200903297003}}.

\bibitem{Sun_2017}
G.~Sun, J.~C. Hewson, D.~O. Lignell, Evaluation of stochastic particle
  dispersion modeling in turbulent round jets, International Journal of
  Multiphase Flow 89 (2017) 108--122.
\newblock \href {http://dx.doi.org/10.1016/j.ijmultiphaseflow.2016.10.005}
  {\path{doi:10.1016/j.ijmultiphaseflow.2016.10.005}}.

\bibitem{Schmidt_2009}
J.~R. Schmidt, J.~O.~L. Wendt, A.~R. Kerstein, Non-equilibrium wall deposition
  of inertial particles in turbulent flow, Journal of Statistical Physics
  137~(2) (2009) 233--257.
\newblock \href {http://dx.doi.org/10.1007/s10955-009-9844-8}
  {\path{doi:10.1007/s10955-009-9844-8}}.

\bibitem{Sun_2014}
G.~Sun, D.~O. Lignell, J.~C. Hewson, C.~R. Gin, Particle dispersion in
  homogeneous turbulence using the one-dimensional turbulence model, Physics of
  Fluids 26~(10) (2014) 103301.
\newblock \href {http://dx.doi.org/10.1063/1.4896555}
  {\path{doi:10.1063/1.4896555}}.
